---
title: "slides"
output:
  xaringan::moon_reader:
    css: ["default", "css/xaringan-themer.css"]
    self_contained: false
    lib_dir: libs
    nature:
      ratio: "16:9"
    seal: false
---

# STAT 436: Statistical Data Visualization

## Spring 2023

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  dpi = 200,
  fig.align = "center",
  out.width = 650,
  fig.height = 3,
  fig.width = 9
  )
th <- theme_minimal() +
  theme(
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "#f7f7f7"),
    panel.border = element_rect(fill = NA, color = "#0c0c0c", size = 0.6),
    axis.text = element_text(size = 14),
    axis.title = element_text(size = 16),
    legend.position = "bottom"
  )
theme_set(th)
options(width = 100)
```

---


### Welcome!!

I'm excited to share this course with you this semester. There are few
activities that engage creative, quantitative, and critical thinking skills all
at once, but data visualization is one of them.

Nothing makes my day like a good data visualization, and I look forward to
seeing those that you create.

---

### Syllabus

* Learning outcomes
* Teaching team and office hours
* Assessments
* Grading

---

### Learning Outcomes

1.	Develop a vocabulary of visual encodings that support exploration of
geospatial, temporal, tree-structured, and network data, and demonstrate
facility implementing them using packages in the R programming language.
1.	Design dynamic queries that support interactive visualization of
heterogeneous data, and demonstrate facility implementing them using the shiny
package in the R programming language.
1.	Design effective visualizations to summarize the results of dimensionality
reduction and clustering algorithms.

---

### Learning Outcomes

1.	Use visual artifacts derived from complex statistical and machine learning
models to discuss the patterns they learn and mistakes they make.
1.	Evaluate strengths and weaknesses of visualizations in relation to the tasks
they support.

---


### Office Hours

Instructor: Kris Sankaran [ksankaran@wisc.edu]

TA: Margaret Turner

We will announce in-person and virtual office hours depending on the results of
this poll: https://go.wisc.edu/43y7f8

---


### Assessments

* In-class exercises and discussions
* 4 Homework assignments
* 3 group project reports and 1 presentation
  - Teams of 4 - 5 people
* 1 midterm exam

---

### Grading

* In-Class Exercises: 15%
* Midterm: 20%
* Homework: 35%
* Group Project: 25%

---

### Class Resources

1. [Canvas page](https://canvas.wisc.edu/courses/346654/modules)
  - Links to all other resources
1. [Readings](https://github.com/krisrs1128/stat436_s23/raw/main/logistics/syllabus.docx) (Page 3)
1. [Piazza](https://canvas.wisc.edu/courses/346654/external_tools/65)
1. [Assignments](https://www.gradescope.com/courses/498858)
1. [Online notes](https://krisrs1128.github.io/stat436_s23/)
1. [Online recordings](https://mediaspace.wisconsin.edu/) (also linked in notes)
1. [Worked code examples](https://github.com/krisrs1128/stat436_s23/tree/main/activities/demos)

---

### Questions?

Also feel free to speak with me after class.

---

### Preparation

* For next lecture, bring your laptops
* Make sure you can run the [starter code](https://github.com/krisrs1128/stat436_s23/blob/main/activities/demos/demo1-1-starter.Rmd) for In-Class Demo [1-1]
  - I recommend using Rstudio
  - You can install the tidyverse package using
  
```{r, eval = FALSE}
install.packages("tidyverse") 
```

---

### Exercise 1-1

1. Introduce yourself to your neighbors. Share your name, degree program, and
one of: a recent hobby, favorite movie, favorite food. Share your chosen
datasets in groups of 2 - 3 people.

1. Submit a response to [Formulating Questions] in the exercise sheet. 

1. We will not grade the plot's quality -- we just want to get a sense of
everyone's starting point.

---

### Exercise 1-1

[Formulating Questions] Pick a dataset from
[TidyTuesday](https://github.com/rfordatascience/tidytuesday#datasets), [Data Is
Plural](https://docs.google.com/spreadsheets/d/1wZhPLMCHKJvwOkP4juclhjFgqIY8fQFMemwKL2c64vk/edit#gid=0),
[Kaggle Datasets](https://www.kaggle.com/datasets), [Google Dataset
Search](https://datasetsearch.research.google.com/), or your own personal
studies that you would like to visualize this semester. 

a. What makes you interested in this dataset? Please provide a link, so we can
use it to create future exercises.

b. Using any tools of your choice, make one example visualization from your
dataset. What question does it help to answer?

---

## January 26, 2023

1. Review Exercise 1 - 1
1. [In-Class Demo 1 - 1]
1. [In-Class Exercise 1 - 2]

---

### Exercise Review

---

---

### [In-Class Demo 1-1](https://github.com/krisrs1128/stat436_s23/blob/main/activities/demos/demo1-1-starter.Rmd)

[London Olympics] The data at this
[link](https://uwmadison.box.com/s/rzw8h2x6dp5693gdbpgxaf2koqijo12l) describes
all participants in the London 2012 Olympics.

a. Create a layered display that shows (i) the ages of athletes across sports
and (ii) the average age within each sport.

b. Sort the sports from lowest to highest average age.

c. Develop one new question based on these data. What makes you interested
in it? Provide a visualization that supports the comparisons needed to
arrive at an answer.
  
---

### Exercise 1-2

Response to *one* of the following questions in the exercise sheet:

* [Critique - Infographic]
* [Critique - Science Paper I]
* [Critique - Science Paper II]

---

## January 31, 2023

---

## February 2, 2023

---

## February 7, 2023

---

## February 9, 2023

---

## February 14, 2023

---

## February 16, 2023

---

## February 21, 2023

---

## February 23, 2023

---

## February 28, 2023

---

## March 2, 2023

---

## March 7, 2023

---

## March 9, 2023

---

## March 21, 2023

---

## March 23, 2023

