---
title: "Untitled"
output: html_document
date: "`r Sys.Date()`"
---

```{r, echo = FALSE}
knitr::opts_chunk$set(warnings = FALSE, message = FALSE)
```

[California Wildfires] In this problem, we will interactively visualize a
[dataset](https://uwmadison.box.com/shared/static/k5vvekf1bhh9e16qb9s66owygc70t7dm.csv)
giving statistics of recent California wildfires. The steps below guide you
through the process of building this visualization.

```{r}
library(tidyverse)
library(shiny)
theme_set(theme_bw())

fires <- read_csv("https://uwmadison.box.com/shared/static/k5vvekf1bhh9e16qb9s66owygc70t7dm.csv") %>%
  mutate(quantile = rank(AcresBurned) / n())
```
    
a. (Static) Plot the day of the year that each fire started against the
county within which it was located. Use the size of the mark to encode the
number of acres burned in each fire.

```{r}
fires
```


```{r, fig.width = 8, fig.height = 6}
counties_order <- fires %>%
  group_by(Counties) %>%
  summarise(total = sum(AcresBurned, na.rm = T)) %>%
  arrange(total) %>%
  pull(Counties)

fires <- fires %>%
  mutate(Counties = factor(Counties, levels = counties_order))

ggplot(fires) +
  geom_point(aes(day_of_year, Counties, size = AcresBurned))
```

b. (Interactive) Provide a way for the viewer to interactively highlight or
reveal details about subsets of fires. For example, introduce a slider to
interactively highlight selected years, a tooltip to highlight the name of a
fire, or a select to search for counties, or a slider to filter by fire
size.

```{r}
dotplot <- function(df) {
  ggplot(df) +
    geom_point(aes(day_of_year, Counties, size = AcresBurned,  col = selected)) +
    scale_color_manual(values = c("#e3e3e3", "orange"))
}

ui <- fluidPage(
  sliderInput("year", "Year", 2013, 2019, c(2013, 2019), sep = ""),
  plotOutput("dotplot", width = 800, height = 500),
  dataTableOutput("table")
)

server <- function(input, output) {
  output$dotplot <- renderPlot({
    fires %>%
      mutate(
        selected = (year >= input$year[1]) & (year <= input$year[2])
      ) %>%
      dotplot()
  })
  
  output$table <- renderDataTable({
    fires %>%
      filter(
        (year >= input$year[1]) & (year <= input$year[2])
      ) %>%
      select(Name, year, AcresBurned, Counties) %>%
      arrange(-AcresBurned)
  })
}

shinyApp(ui, server)
```

c. Introduce at least one other UI output. For example, print a table of the
selected fires, interactively print summary statistics, or show a histogram
of fire sizes. Sketch the reactivity graph associated with your application.

```{r}
ui <- fluidPage(
  sliderInput("year", "Year", 2013, 2019, c(2013, 2019), sep = ""),
  plotOutput("dotplot", width = 800, height = 500)
)

server <- function(input, output) {
  # fill this part in
}

shinyApp(ui, server)
```
