---
title: "Untitled"
output: html_document
date: "`r Sys.Date()`"
---

```{r}
knitr::opts_chunk$set(warnings = FALSE, message = FALSE)
```


[Plant Growth Experiment] This problem will give you practice with tidying a
dataset so that it can be easily visualized. The data describe the height of
several plants measured every 7 days. The plants have been treated with
different amounts of a growth stimulant. The first few rows are printed below --
`height.x` denotes the height of the plant on day `x`.

```{r}
library(tidyverse)
plants <- read_csv("https://uwmadison.box.com/shared/static/qg9gwk2ldjdtcmmmiropcunf34ddonya.csv")
plants
```

a. Propose an alternative arrangement of rows and columns that conforms to the
tidy data principle.

| treatment | plant_id | time | height
| ... | ... | 0 | ...
| ... | ... | 7 | ...
| ... | ... | 14 | ...
| ... | ... | 21 | ...

b. Implement your proposed arrangement from part (a).

```{r}
plants %>%
  pivot_longer(c("height.0", "height.7", "height.14", "height.21"))

plants %>%
  pivot_longer(paste0("height.", c(0, 7, 14, 21)))

plants_long <- plants %>%
  pivot_longer(starts_with("height")) %>%
  mutate(
    day = as.integer(str_extract(name, "[0-9]+"))
  )
  
plants_long
```

c. Using the dataset from (b), design and implement a visualization showing the
growth of the plants over time according to different treatments.


```{r}
theme_set(theme_classic())
ggplot(plants_long, aes(day, value, col = treatment)) +
  geom_line(aes(group = plantid)) +
  geom_point() +
  scale_color_brewer(palette = "Set2") +
  facet_wrap(~ treatment)

```


[NYC Flights Summaries] The following questions refer to the NYC flights
dataset. The first few lines are printed below.

```{r}
library(nycflights13)
flights %>% select(carrier, air_time, distance)
```

a. Provide code to create a new column giving the average speed of
the flight: $\texttt{speed} := \frac{\texttt{distance}}{\texttt{air\_time}}$.

```{r}
flights %>%
  mutate(speed = distance / air_time)
```

b. Is there a large variation in flight speed across carriers? Design
and sketch code for a visualization that could be used to answer this
question (you may assume the output of (a)).


```{r}
flights %>%
  mutate(speed = distance / air_time) %>%
  ggplot() +
  geom_boxplot(aes(speed, reorder(carrier, speed, median, na.rm = T)))
  #geom_boxplot(aes(speed, carrier))

flights %>%
  mutate(speed = distance / air_time) %>%
  ggplot() +
  geom_point(
    aes(speed, reorder(carrier, speed, median, na.rm = T)),
    alpha = 0.05, size = 0.5, position = position_jitter(h = 0.1)
    )
```




```{r, fig.height = 3, fig.width = 10}
flights %>%
  mutate(speed = distance / air_time) %>%
  ggplot() +
  geom_histogram(aes(speed)) +
  facet_wrap(~ reorder(carrier, speed, mean, na.rm = TRUE), ncol = 8)

```

