---
title: "Untitled"
output: html_document
date: "`r Sys.Date()`"
---

```{r, echo = FALSE}
knitr::opts_chunk$set(warnings = FALSE, message = FALSE)
```

```{r}
library(sf)
library(tmap)
library(tidyverse)
library(ceramic)
theme_set(theme_bw())
```

[Glacial Lakes]. The data at this [link](https://raw.githubusercontent.com/krisrs1128/stat436_s23/main/data/GL_3basins_2015.topojson) contain labels of glacial lakes the
Hindu Kush Himalaya, created during an ecological survey in 2015 by the
International Centre for Integrated Mountain Development.

```{r}
lakes <- read_sf("https://raw.githubusercontent.com/krisrs1128/stat436_s23/main/data/GL_3basins_2015.topojson") %>%
  mutate(log_area = log(Area))

cols <- c("#023859", "#99ADBF")


lakes

```

a. How many lakes are in this dataset? What are the latitude / longitude
coordinates of the largest lakes in each Sub-basin?

```{r}
nrow(lakes)

lakes %>%
  group_by(Sub_Basin) %>%
  summarise(max(Area))
```


```{r}
lakes %>%
  group_by(Sub_Basin) %>%
  slice_max(Area)

top_lakes <- lakes %>%
  group_by(Sub_Basin) %>%
  filter(Area == max(Area))

```

b. Plot the polygons associated with each of the lakes identified in step
(a). _Hint: You may find it useful to split lakes across panels using the
`tmap_facets` function. If you use this approach, make sure to include a
scale with `tm_scale_bar()`, so that it is clear that lakes have different
sizes.

```{r}
# find the order of the sub_basins
basin_order <- top_lakes %>%
  arrange(-Area) %>%
  pull(Sub_Basin)

# create factor levels that reflect the order
top_lakes <- top_lakes %>%
  mutate(Sub_Basin = factor(Sub_Basin, levels = basin_order))

tm_shape(top_lakes) +
  tm_polygons(col = cols[1]) +
  tm_facets("Sub_Basin") + 
  tm_scale_bar()



```

c. Visualize all lakes with latitude between 28.2 and 28.4 and with
longitude between 85.8 and 86. Optionally, add a basemap associated with
each lake.

```{r}
lakes_subset <- lakes %>%
  filter(
    Latitude >= 28.2, Latitude <= 28.4,
    Longitude >= 85.8, Longitude <= 86
  )

tm_shape(lakes_subset) +
  tm_polygons(col = cols[1])

```


```{r}
Sys.setenv(MAPBOX_API_KEY="pk.eyJ1Ijoia3Jpc3JzMTEyOCIsImEiOiJjbDYzdjJzczQya3JzM2Jtb2E0NWU1a3B3In0.Mk4-pmKi_klg3EKfTw-JbQ")
basemap <- cc_location(cbind(85.9, 28.3), buffer = 1e4)

tm_shape(basemap) +
  tm_raster()

tm_shape(basemap) +
  tm_rgb() +
  tm_shape(lakes_subset) +
  tm_polygons(col = cols[1])
```










