---
title: "Untitled"
output: html_document
date: "`r Sys.Date()`"
---

The data below measures properties of various Antarctic penguins.

```{r, echo = TRUE}
library(tidyverse)
theme_set(theme_bw())
penguins <- read_csv("https://uwmadison.box.com/shared/static/ijh7iipc9ect1jf0z8qa2n3j7dgem1gh.csv")
penguins
```

Create a single plot that makes it easy to answer both of these questions, (i)
How is bill length related to bill depth within and across species? (ii) On
which islands are which species found?


X Bill length vs Depth -> Scatterplot
  - ggplot()
  - geom_point()
  - aes(bill length and depth)

Across species -> Colors
  - aes(add color)


Different islands -> Shape
  - aes(add shape)


```{r, fig.width = 6, fig.height = 5}
ggplot(penguins) +
  geom_point(aes(bill_length_mm, bill_depth_mm, col = species, shape = island), size = 3, alpha = 0.5) +
  labs(x = "Bill Length (mm)", y = "Bill Depth (mm)", col = "Species", shape = "Island", title = "Bill Properties across Species")
```


```{r, fig.width = 6, fig.height = 3}
ggplot(penguins, aes(bill_length_mm, bill_depth_mm)) +
  stat_smooth(method = "lm", col = "#0c0c0c", alpha = 0.2, size = 0.4) +
  stat_smooth(aes(col = species, fill = species), method = "lm", alpha = 0.2, size = 0.4) +
  geom_point(aes(col = species), size = 1) +
  facet_wrap(vars(island)) +
  labs(x = "Bill Length (mm)", y = "Bill Depth (mm)", col = "Species", shape = "Island", title = "Bill Properties across Species")
```



















