---
title: "Untitled"
output: html_document
date: "`r Sys.Date()`"
---

```{r}
knitr::opts_chunk$set(warnings = FALSE, message = FALSE)
```

[Pokemon]  This problem gives practice in deriving new variables to improve a
faceted plot. The data below give attack and defense statistics for Pokemon,
along with their types. We will build a visualization to answer the question --
how do the different types of Pokemon vary in their attack and defense
potential?

```{r}
library(tidyverse)
pokemon <- read_csv("https://uwmadison.box.com/shared/static/hf5cmx3ew3ch0v6t0c2x56838er1lt2c.csv")
```
    
a. Derive a new column containing the attack-to-defense ratio, defined as
$\frac{\text{Attack}}{\text{Defense}}$.

```{r}
pokemon <- pokemon %>%
  mutate(attack_to_defense = Attack / Defense)
```



b. For each `type_1` group of Pokemon, compute the median attack-to-defense
ratio.

```{r}
type_1_order <- pokemon %>%
  group_by(type_1) %>%
  summarise(attack_to_defense = median(attack_to_defense)) %>%
  arrange(attack_to_defense) %>%
  pull(type_1)
```


c. Plot the attack vs. defense scores for each Pokemon, faceted by `type_1`. Use
the result of (b) to ensure that the panels are sorted from types with highest
to lowest attack-to-defense ratio.

```{r}
ggplot(pokemon) +
  facet_wrap(~ reorder(type_1, attack_to_defense, median)) +
  geom_point(aes(Attack, Defense))
```
```{r}
pokemon
```


```{r}
pokemon <- pokemon %>%
  mutate(type_1 = factor(type_1, levels = type_1_order))
```


```{r, fig.width = 5, fig.height = 3}
ggplot(pokemon, aes(Attack, Defense)) +
  facet_wrap(~ type_1) +
  stat_smooth(method = "lm", col = "black") +
#  scale_color_gradient2(midpoint = 100, mid = "green") +
  scale_color_manual(values = )
  geom_point(aes(col = type_1), alpha = 0.6)
```


d. Propose, but do not implement, a visualization of this dataset that makes use
of dynamic queries. What questions would the visualization answer? What would be
the structure of interaction, and how would the display update when the user
provides a cue?